%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage{fancyhdr}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
% \usepackage{fontawesome} % not used in body; uncomment if icons added
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable / ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{2pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Jiehan Liu} \\ \vspace{3pt}
    \small
    Encina Hall, 616 Jane Stanford Way, Stanford, CA 94305
    $|$
    \hspace{.5pt} \href{mailto:jiehanl@stanford.edu}{jiehanl@stanford.edu}
    $|$
    \hspace{.5pt} \href{https://jiehanL.github.io}{jiehanL.github.io}
\end{center}


%---------- RESEARCH INTERESTS ----------

\section{Research Interests}
  \vspace{1pt}
  \small Political methodology; measurement; high-dimensional data and machine learning for social science; estimation of heterogeneous treatment effects. Substantive applications in political behavior, public opinion, and the political consequences of generative AI.


%---------- EDUCATION ----------

\section{Education}
  \vspace{1pt}
  \resumeSubHeadingListStart

    \resumeEducationHeading
      {Stanford University}{Stanford, CA}
      {Ph.D.\ in Political Science (Political Methodology; Comparative Politics)}{Sep.\ 2024 \textbf{--} Aug.\ 2029 (expected)}

    \resumeEducationHeading
      {The University of Chicago}{Chicago, IL}
      {M.A.\ in Computational Social Science}{Sep.\ 2021 \textbf{--} Aug.\ 2023}

    \resumeEducationHeading
      {Jilin University}{Changchun, China}
      {B.A.\ in International Politics; B.S.\ in Computer Science}{Jun.\ 2017 \textbf{--} Jun.\ 2021}

  \resumeSubHeadingListEnd


%---------- PUBLICATIONS ----------

\section{Publications}
  \vspace{2pt}

  \textit{\small Peer-Reviewed Articles}
  \resumeSubHeadingListStart
    \small\item Offer-Westort, M., \textbf{Liu, J.}, Feamster, N., Garg, K., Hoang, N.\ P., \& Hosamane, S.\ (2026). Deep canvassing with automated conversational agents: Personalized messaging to change attitudes. \textit{Research \& Politics}, 13(1), 20531680251414926.
  \resumeSubHeadingListEnd

  \vspace{2pt}
  \textit{\small Working Papers}
  \resumeSubHeadingListStart
    \small\item \textbf{Liu, J.}, Liu, Z., \& Xu, Y.\ (2025). A Practical Guide to Estimating Conditional Marginal Effects: Modern Approaches. \textit{arXiv:2504.01355}.
    \small\item Hainmueller, J., \textbf{Liu, J.}, Liu, Z., Mummolo, J., \& Xu, Y.\ (2025). A Response to Recent Critiques of Hainmueller, Mummolo and Xu (2019) on Estimating Conditional Relationships. \textit{arXiv:2502.05717}.
    \small\item Westwood, S.\ J., Grimmer, J., Hall, A.\ B., Flanigan, B., \& \textbf{Liu, J.} Measuring Perceived Slant in Large Language Models Through User Evaluations.
  \resumeSubHeadingListEnd

  \vspace{2pt}
  \textit{\small Work in Progress}
  \resumeSubHeadingListStart
    \small\item \textbf{Liu, J.} Auditing Measurement Uncertainty in LLM-Based Text Coding.
  \resumeSubHeadingListEnd


%---------- TEACHING ----------

\section{Teaching}
  \vspace{1pt}
  \resumeSubHeadingListStart
    \small\item \textbf{Teaching Assistant, Stanford University.}
      \begin{itemize}[leftmargin=0.25in, itemsep=-1pt]
        \small\item POLISCI 1, \textit{The Science of Politics} --- Fall 2025 (Instructors: E.\ Chapman, S.\ Paci).
        \small\item POLISCI 157, \textit{The Politics of AI} --- Summer 2026 (Instructor: S.\ Paci).
      \end{itemize}
    \vspace{1pt}
    \small\item \textbf{Tutorial.} \textit{interflex}: Conditional Marginal Effects in R (2025) --- documentation for the companion R package to Liu, Liu, \& Xu (2025).
  \resumeSubHeadingListEnd


%---------- CONFERENCE PRESENTATIONS ----------

\section{Conference Presentations}
  \vspace{1pt}
  \resumeSubHeadingListStart
    \small\item \textit{Auditing Measurement Uncertainty in LLM-Based Text Coding.} 43rd Annual Summer Meeting of the Society for Political Methodology (PolMeth), 2026 (forthcoming).
    \small\item \textit{Bots with Bites: Social Media Robots and Autocratic Surviving Strategies.} 80th Annual Midwest Political Science Association Conference, Chicago, IL, April 2023.
  \resumeSubHeadingListEnd


%---------- HONORS & AWARDS ----------

\section{Honors \& Awards}
  \vspace{1pt}
  \resumeSubHeadingListStart
    \small\item \textbf{EDGE Doctoral Fellowship}, Stanford University, 2024.
    \small\item \textbf{H\&S Dean's Scholars Fellowship}, Stanford University, 2024--2029.
    \small\item \textbf{Maroon Scholar Research Award}, The University of Chicago, 2021, 2022.
    \small\item \textbf{China National Scholarship}, Ministry of Education of China (top 0.2\% of students), 2020.
  \resumeSubHeadingListEnd


%---------- SELECTED GRADUATE COURSEWORK ----------

\section{Selected Graduate Coursework}
  \vspace{1pt}
  \resumeSubHeadingListStart
    \small\item Causal Inference; Advanced Topics in Causal Inference; Linear Models; Applied Longitudinal Data Analysis; Large-Scale Computing for the Social Sciences; Political Regimes and Transitions.
  \resumeSubHeadingListEnd


%---------- SKILLS & LANGUAGES ----------

\section{Skills \& Languages}
  \vspace{1pt}
  \resumeSubHeadingListStart
    \small\item \textbf{Statistical computing:} R, Stata, Stan. \textbf{Programming:} Python, SQL, C, Java, JavaScript; Git, Docker, AWS, QGIS, \LaTeX.
    \small\item \textbf{Languages:} Mandarin (native), English (professional), Russian (elementary).
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
